---
title: "Some more analyses for the StatLearn MetaAnalysis"
author: "Alexis Black & Christina Bergmann"
date: "2/1/2017"
output: html_document
---

## Set-up

This is the same as in the main analyses to create comparable datasets
```{r SetUp, echo = FALSE}

library(tidyverse)

#setwd("~/Dropbox/StatLearnDB") #If you need to set the working directory


library(metafor)

#### Get data ####

#run Effect-size script first
source("scripts/calculateES.R")

#### Some clean-up ####
db <-
  db %>% 
  mutate(StimuliType = ifelse(test_lang_program=="natural", "1", "0")) %>% 
  mutate(StimuliType = as.factor(StimuliType)) %>% 
  mutate(age.C = mean_age_1-mean(mean_age_1, na.rm=TRUE)) %>% 
  rename(gender = gender_1)


db$collapse <- paste(db$study_ID, db$expt_num, db$same_infant, sep = "_")

for(independent in unique(db$collapse)){
  if(length(db[db$collapse==independent])>1){
    sub = db[db$collapse==independent, ]
    sub$d_calc <- median(sub$d_calc)
    sub$d_var_calc <- median(sub$d_var_calc)
    sub$g_calc <- median(sub$g_calc)
    sub$g_var_calc <- median(sub$g_var_calc)
    sub$corr_imputed <- median(sub$corr_imputed)
    db <- db[!(db$collapse==independent),]
    db <- rbind(db, sub[1,])
  }
}




#### Create subsets ####

# direct replications only, as coded in the spreadsheet

db_DR <-
  db %>% 
  filter(DirectRep == "yes")
```
# What could we look at in the future?

- What are some of the potential moderators?
  + **familiarization time**
  + frequency_balanced (based on cursory look, might be worth exploring)
  + ForwardTP_nonword
  + number_syllables
  + duration_syllables
  + **gender**
  
- Obviously, we won't have enough power to look at all of these. How do we choose?

#Gender
```{r Gender}


# Look at Gender
rma_gender=rma.mv(g_calc, g_var_calc, mods=gender, data=db, random = ~ 1|short_cite)
summary(rma_gender)

# Let's take a look at this graphically
dat <-
  db %>% 
  rename(cite = short_cite,
         yi = g_calc,
         vi = g_var_calc) %>% 
  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
  filter(gender >.01) %>% 
  arrange(desc(gender))
dat$se = sqrt(dat$vi)
dat$lowerci = (-1.96*dat$se)+dat$yi
dat$upperci = (1.96*dat$se)+dat$yi

ggplot(dat, aes(y=reorder(study_ref, -gender), x=yi, xmin=lowerci, xmax=upperci))+
  geom_point(aes(color = gender))+
  geom_errorbarh(height=.1)+
  scale_x_continuous(limits=c(-1.5,1.5), name='Standardized Mean Difference (g)')+
  ylab('Reference')+
  geom_vline(xintercept=0, color='grey', linetype='dashed')+
  geom_vline(xintercept=0.65, color='black', linetype='dashed')

```


#Different Cues

```{r}
db_stress <-
  db %>% 
  filter(additional_cue == c("stress", "intensity", "duration"))
rma_stress <- rma.mv(g_calc, g_var_calc, mods = ~factor(cue_conflict_TP)-1, data = db_stress, random = ~1|short_cite)
summary(rma_stress)
```

Before I get too excited - only 6 rows of data?? That makes no sense. Why would that happen? Ok, let's subset a different way.

```{r}
db_stress <- subset(db, additional_cue == "stress" | additional_cue == "intensity" |
                      additional_cue == "duration" | additional_cue == "prime, stress")
rma_stress <- rma.mv(g_calc, g_var_calc, mods = ~factor(cue_conflict_TP)-1, data = db_stress, random = ~1|short_cite)
summary(rma_stress)
```

And, not even close. This is something to bring up in the discussion. 

#Familiarization Duration
```{r}
rma_duration <- rma.mv(g_calc, g_var_calc, mods = familiarization_time, 
                       data = db, 
                       random = ~1|short_cite)
summary(rma_duration)
```

Would be good to look at the interactions of all of these things though ...

# Take out the direct reps, bc maybe they skew what would otherwise be a familiarity preference in the rest of the data

```{r}
db_nonDR <-
  db %>% 
  filter(DirectRep == "no")

rma_nonDR <- rma.mv(g_calc, g_var_calc,  
                       data = db_nonDR, 
                       random = ~1|short_cite)
summary(rma_nonDR)
```




## Future ideas
- I'd like to explore the studies demonstrating a familiarity preference. Are they a unique class? Or is it 'predictable' random variation around the mean? Given the outliers in our funnel plots and the extreme degree of heterogeneity, I wonder if there are multiple things going on (rather, I think there are multiple things going on, can we figure out what they are?)


